### 2018-12-29 papers/journal/experiments.tex
Experiments section update-2

\subsection{Implementation}
{\sattool} is based on the architecture of a Bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
%
{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
%
{\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
%
The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool}.
%
All the experiments were done on a machine with  Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM with 30 min (1800 sec) timeout.

@@

\textbf{{\sattool} (Bounded model checker based tool)}:
	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
\todo{SA: CBMC Diagram}	
The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%

In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\input{synth-table}
We have implemented the synthesis encodings (presented in section 6.6) in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can not only synthesize the discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.

@@

In table~\ref{tab:smt-grph} we present the minimal connectivity results for each variation of the existential condition. 
%
Table~\ref{tab:satsmt-graph} present the comparision of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we fixed the total number of molecules ($|M|$) to be $2|N|$ 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation F, of 2-connected 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
%
In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologicly relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.

\input{qbf-table}
%\textbf{Universal Condition:}
\todo{SA: Will add after experimentations.}
Table~\ref{tab:qbf-graph} presents the result of the QBF tool.

%\textbf{Synthesis}:

>>>>

\subsection{Implementation}
{\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
%
{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
%
{\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
%
The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool}.
%
All the experiments were done on a machine with  Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM with 30 min (1800 sec) timeout.

@@

\textbf{{\sattool} (bounded model checker based tool)}:
	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
\todo{SA: Do we need a diagram}	
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

We encode the problem using CBMC C-language front-end (CFE) interface 
%ANSI-C programs 
with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%	
In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked.

Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\input{synth-table}
We have implemented the synthesis encodings (presented in section 6.6) in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can not only synthesize the discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

@@

In table~\ref{tab:smt-grph} we present the minimal connectivity results for each variation of the existential condition. 
%
Table~\ref{tab:satsmt-graph} present the comparision of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we fixed the total number of molecules ($|M|$) to be $2|N|$ 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%
In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation F of 2-connected, 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.

\input{qbf-table}
%\textbf{Universal Condition:}
\todo{SA: will improve after experimentation.}
Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The table represents the result of the graph connectivity for each variation of the VTS.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
% 
The experimentations were done using two QBF solvers: \depqbf and \rarqbf.

%(there is a satisfying assignments to satisfy constraints of VTS) is valid VTS.   
%\textbf{Synthesis}:
